### 2019-07-31 paper_06_milestone/1st/article.tex
Typeset paper6

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_scheme_mixing}
\caption{Scheme representing the effect of mixing on the density profile and the center of mass.}
\label{fig:average:mixing}
\end{figure}

@@

\caption{Top: scheme of the experimental setup for the MILESTONE 2017
experiments (see text for description). Center: photography of the experiment.
Bottom: chronogram of the position of the carriage $x_c(t)$.}

\label{fig:exp}
\end{figure}

@@

\begin{figure}[htp!]
\includegraphics[width=80mm]{tmp/fig_energy_vs_time}
\label{fig:energy:vs:time}

\caption{Kinetic energy decay for experiment M16-73.}

@@

\begin{figure}[htp!]
\includegraphics[width=80mm]{tmp/fig_fit_EK}
\label{fig:fit:EK}

\caption{Fits of the kinetic energy decay for M16-73 (same as in
figure~\ref{fig:energy:vs:time}). The time derivatives of the kinetic energy in
(b) are normalized by $\eps_c = U_c^3 / D_c$.}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_R_vs_Fh}
\label{fig:RvsFh}

\caption{Evaluation of the buoyancy Reynolds number $\R$ and the horizontal
Froude number $F_h$ from the horizontal kinetic energy $E_{Kh}$ and its decay
$\eps_m = \mean{d_t E_{Kh}}$ for the M16 experiments.}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_R_vs_Fh_other_studies_with_milestone17}
\label{fig:RvsFh:other}

\caption{Buoyancy Reynolds number $\R$ versus horizontal Froude number $F_h$
for few M16 and M17 experiments and for other experimental and numerical
studies of stratified turbulence.}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_rho_vs_time}\\
\includegraphics[width=\figwidth]{tmp/fig_rho_vs_time_corrected}
\label{fig:rho:vs:time}

\caption{Density signals measured by the 5 density probes for experiment M17-21
corresponding to $D = 0.5$~m, $N=0.55$~rad/s and $U=12$~cm/s. Three probes are
attached to vertical profilers. The two other fixed probes are at the top and
at the bottom, respectively. (a) raw signals and (b) signals corrected to
compensate a derive of the probes.
}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_profiles_mixing}\\
\includegraphics[width=\figwidth]{tmp/fig_profiles_probe_averaged}
\label{fig:profiles:mixing}

\caption{Evolution of the density profiles for experiment M17-21 corresponding
to $D = 0.5$~m, $N=0.55$~rad/s and $U=12$~cm/s.}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_energy_pot_vs_time}
\label{fig:energy:pot:vs:time}

\caption{Evolution of the normalized potential energy for experiment M17-21
corresponding to $D = 0.5$~m, $N=0.55$~rad/s and $U=12$~cm/s.}

@@

\begin{figure}[htp!]
\includegraphics[width=\figwidth]{tmp/fig_dt_pot_energy}
\label{fig:dt:pot:energy}

\caption{Normalized mixing coefficient $\eps_P / (3\times10^{-3} {U_c}^3/D_c)$
for some MILESTONE 17 experiments.}

>>>>

\begin{figure}[htp!]
\centering
\includegraphics[width=\figwidth]{tmp/fig_scheme_mixing}
\caption{Scheme representing the effect of mixing on the density profile and
the center of mass.}%
\label{fig:average:mixing}
\end{figure}

@@

\caption{Top: scheme of the experimental setup for the MILESTONE 2017
experiments (see text for description). Center: photography of the experiment.
Bottom: chronogram of the position of the carriage $x_c(t)$.}%
\label{fig:exp}
\end{figure}

@@

\begin{figure}[htp!]
\centering
\includegraphics[width=0.5\textwidth]{tmp/fig_energy_vs_time}

\caption{Kinetic energy decay for experiment M16-73.}%
\label{fig:energy:vs:time}

@@

\begin{figure}[htp!]
\centering
\includegraphics[width=80mm]{tmp/fig_fit_EK}

\caption{Fits of the kinetic energy decay for M16-73 (same as in
figure~\ref{fig:energy:vs:time}). The time derivatives of the kinetic energy in
(b) are normalized by $\eps_c = U_c^3 / D_c$.}%
\label{fig:fit:EK}

@@

\begin{figure}[htp!]
\centering
\includegraphics[width=\figwidth]{tmp/fig_R_vs_Fh}%

\caption{Evaluation of the buoyancy Reynolds number $\R$ and the horizontal
Froude number $F_h$ from the horizontal kinetic energy $E_{Kh}$ and its decay
$\eps_m = \mean{d_t E_{Kh}}$ for the M16 experiments.}%
\label{fig:RvsFh}

@@

\begin{figure}[htp!]
\centering
\includegraphics[width=\figwidth]{tmp/fig_R_vs_Fh_other_studies_with_milestone17}%

\caption{Buoyancy Reynolds number $\R$ versus horizontal Froude number $F_h$
for few M16 and M17 experiments and for other experimental and numerical
studies of stratified turbulence.}%
\label{fig:RvsFh:other}

@@

\begin{figure}[htp!]
\centering
\includegraphics[width=0.7\textwidth]{tmp/fig_rho_vs_time}\\
\includegraphics[width=0.7\textwidth]{tmp/fig_rho_vs_time_corrected}

\caption{Density signals measured by the 5 density probes for experiment M17-21
corresponding to $D = 0.5$~m, $N=0.55$~rad/s and $U=12$~cm/s. Three probes are
attached to vertical profilers. The two other fixed probes are at the top and
at the bottom, respectively. (a) raw signals and (b) signals corrected to
compensate a derive of the probes.
}%
\label{fig:rho:vs:time}

@@

\begin{figure}[htp!]
\centering
\includegraphics[width=0.7\figwidth]{tmp/fig_profiles_mixing}
\includegraphics[width=0.7\figwidth]{tmp/fig_profiles_probe_averaged}

\caption{Evolution of the density profiles for experiment M17-21 corresponding
to $D = 0.5$~m, $N=0.55$~rad/s and $U=12$~cm/s.}%
\label{fig:profiles:mixing}

@@

\begin{figure}[htp!]
\centering
\includegraphics[width=0.7\figwidth]{tmp/fig_energy_pot_vs_time}

\caption{Evolution of the normalized potential energy for experiment M17-21
corresponding to $D = 0.5$~m, $N=0.55$~rad/s and $U=12$~cm/s.}%
\label{fig:energy:pot:vs:time}

@@

\begin{figure}[htp!]
\centering
\includegraphics[width=\figwidth]{tmp/fig_dt_pot_energy}

\caption{Normalized mixing coefficient $\eps_P / (3\times10^{-3} {U_c}^3/D_c)$
for some MILESTONE 17 experiments.}%
\label{fig:dt:pot:energy}
